---
title: "decone: An easy-to-use and comprehensive evaluation toolkit for cell type deconvolution from expression data"
author: Wei Zhang
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{decone: An easy-to-use and comprehensive evaluation toolkit for cell type deconvolution from expression data}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Cell type proportion is related with certain phenotype or disease ([Wei, *et al.*](https://doi.org/10.1093/bib/bbab362)). Therefore, quantifying cell or tissue proportions is an important problem in bioinformatics.

Here, we proposed a cell type <u>decon</u>volution <u>e</u>valuating toolkit named '**decone**' to perform comprehensive and systematic analysis for different algorithms.

**decone** consists of 6 main part functions as below.

+ Pseudo bulk data generation (including bulk and single cell).
+ Stability analysis under different types of noise.
+ Rare component analysis.
+ Unknown component analysis.
+ Comprehensive evaluation metrics.
+ Well characterized datasets for deconvolution utilities.


For more information, please see [decone github page](https://github.com/Honchkrow/decone).

```{r setup}
library(decone)

sessionInfo()
```
